---
title: "RWorksheet#5_group9"
output: pdf_document
date: "2023-11-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#JIRRAINE OCTAVIANO
#BARBIE JOY OBAS
#MEIGELYN JOY MATIAS
#ANDREA PATRICE PINEDA
```

############  Web Scraping IMDB TV Shows #################

```{r}

install.packages("tidyverse")
install.packages("dplyr")
install.packages("rvest")
install.packages("httr")
install.packages("polite")
install.packages("ggplot2")
install.packages("kableExtra")
library(tidyverse)
library(dplyr)
library(rvest)
library(httr)
library(polite)
library(ggplot2)
library(kableExtra)

polite::use_manners(save_as = 'polite_scrape.R')

```
1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the
tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.
```{r}
#creating objects for the dataset
rank <- character(50)
title <-character(50)
peoples_vote <- character(50)
episodes <- character(50)
year <- character(50)

url <- "https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250"
session <- bow(url, user_agent= "Educational Purposes")
session

#Ranks
rank <- scrape(session) %>% 
  html_nodes('h3.ipc-title__text') %>% 
  html_text()
rank[1:51]

#Titles
titles <- scrape(session) %>%
  html_nodes("h3.ipc-title__text") %>%
  html_text()
titles50 <- titles[2:51]

#Ratings
ratings <- scrape(session) %>%
  html_nodes("span.ipc-rating-star.ipc-rating-star--base.ipc-rating-star--imdb.ratingGroup--imdb-rating") %>%
  html_text()

cleaned_ratings <- substr(ratings, 1, 3)
ratings50 <- cleaned_ratings[1:50]

#Peoples vote
people_vote <- scrape(session) %>%
  html_nodes("span.ipc-rating-star--voteCount") %>%
  html_text()

people_vote50 <- people_vote[1:50]
cleaned_vote <- gsub("\\(|\\)", "", people_vote50)

#Episodes
episodes <- scrape(session) %>%
  html_nodes("span.sc-43986a27-8:nth-of-type(2)") %>%
  html_text()
episodes50 <- episodes[1:50]

#Year
year <- scrape(session) %>%
  html_nodes("span.sc-43986a27-8:nth-of-type(1)") %>%
  html_text()
year50 <- year[1:50]

#Dataframe
TopTv_df <- data.frame(
  Ranks = rank[1:50],  # Correct variable name
  Titles = titles50,
  Ratings = ratings50,
  People_Votes = cleaned_vote,
  Episodes = episodes50,
  Year = year50
)
TopTv_df

```
2. From the 50 tv shows, select at least 5 tv shows to scrape the user reviews that will include the
reviewer’s name, date of reviewed, user rating, title of the review, and text reviews.

 1st Link
```{r}

pad_with_na <- function(vec, target_length) {
  if (length(vec) < target_length) {
    return(c(vec, rep(NA, target_length - length(vec))))
  } else {
    return(vec)
  }
}


OP_Link <- "https://www.imdb.com/title/tt9253866/reviews?ref_=tt_urv"
session2 <- bow(OP_Link, user_agent = "Educational Purposes")


OP_Title <- scrape(session2) %>%
  html_nodes("a[itemprop='url']") %>%
  html_text()

OP_RevName <- scrape(session2) %>%
  html_nodes(".display-name-link a") %>%
  html_text()

OP_RevDate <- scrape(session2) %>%
  html_nodes("span.review-date") %>%
  html_text()

OP_UserRating <- scrape(session2) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()

OP_TitleRev <- scrape(session2) %>%
  html_nodes("a.title") %>%
  html_text() %>%
  gsub("\n ", "", .)

OP_TextRev <- scrape(session2) %>%
  html_nodes("div.text") %>%
  html_text()


max_length <- max(
  length(OP_Title),
  length(OP_RevName),
  length(OP_RevDate),
  length(OP_UserRating),
  length(OP_TitleRev),
  length(OP_TextRev)
)

OP_Title <- pad_with_na(OP_Title, max_length)
OP_RevName <- pad_with_na(OP_RevName, max_length)
OP_RevDate <- pad_with_na(OP_RevDate, max_length)
OP_UserRating <- pad_with_na(OP_UserRating, max_length)
OP_TitleRev <- pad_with_na(OP_TitleRev, max_length)
OP_TextRev <- pad_with_na(OP_TextRev, max_length)


OP_Df <- data.frame(
  Tv_Shows = OP_Title,
  Reviewer_Name = OP_RevName,
  Reviewer_Date = OP_RevDate,
  Reviewer_Rating = OP_UserRating,
  Title_Review = OP_TitleRev,
  Text_Review = OP_TextRev
)

head(OP_Df)


```
2nd Link
```{r}
pad_with_na <- function(vec, target_length) {
  if (length(vec) < target_length) {
    return(c(vec, rep(NA, target_length - length(vec))))
  } else {
    return(vec)
  }
}


GT_Link <- "https://www.imdb.com/title/tt1865718/reviews?ref_=tt_urv"
session2 <- bow(GT_Link, user_agent = "Educational Purposes")


GT_Title <- scrape(session2) %>%
  html_nodes(".parent a") %>%
  html_text()

GT_RevName <- scrape(session2) %>%
  html_nodes(".display-name-link") %>%
  html_text()

GT_RevDate <- scrape(session2) %>%
  html_nodes("span.review-date") %>%
  html_text()

GT_UserRating <- scrape(session2) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()

GT_TitleRev <- scrape(session2) %>%
  html_nodes("a.title") %>%
  html_text() %>%
  gsub("\n ", "", .)

GT_TextRev <- scrape(session2) %>%
  html_nodes("div.text") %>%
  html_text()


max_length <- max(
  length(GT_Title),
  length(GT_RevName),
  length(GT_RevDate),
  length(GT_UserRating),
  length(GT_TitleRev),
  length(GT_TextRev)
)

GT_Title <- pad_with_na(GT_Title, max_length)
GT_RevName <- pad_with_na(GT_RevName, max_length)
GT_RevDate <- pad_with_na(GT_RevDate, max_length)
GT_UserRating <- pad_with_na(GT_UserRating, max_length)
GT_TitleRev <- pad_with_na(GT_TitleRev, max_length)
GT_TextRev <- pad_with_na(GT_TextRev, max_length)


GT_Df <- data.frame(
  Tv_Shows = GT_Title,
  Reviewer_Name = GT_RevName,
  Reviewer_Date = GT_RevDate,
  Reviewer_Rating = GT_UserRating,
  Title_Review = GT_TitleRev,
  Text_Review = GT_TextRev
)

head(GT_Df)


```
3rd Link
```{r}
pad_with_na <- function(vec, target_length) {
  if (length(vec) < target_length) {
    return(c(vec, rep(NA, target_length - length(vec))))
  } else {
    return(vec)
  }
}

DN_Link <- "https://www.imdb.com/title/tt0877057/reviews?ref_=tt_urv"
session2 <- bow(DN_Link, user_agent = "Educational Purposes")


DN_Title <- scrape(session2) %>%
  html_nodes(".parent a") %>%
  html_text()

DN_RevName <- scrape(session2) %>%
  html_nodes(".display-name-link") %>%
  html_text()
DN_RevDate <- scrape(session2) %>%
  html_nodes("span.review-date") %>%
  html_text()

DN_UserRating <- scrape(session2) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()

DN_TitleRev <- scrape(session2) %>%
  html_nodes("a.title") %>%
  html_text() %>%
  gsub("\n ", "", .)

DN_TextRev <- scrape(session2) %>%
  html_nodes("div.text") %>%
  html_text()


max_length <- max(
  length(DN_Title),
  length(DN_RevName),
  length(DN_RevDate),
  length(DN_UserRating),
  length(DN_TitleRev),
  length(DN_TextRev)
)

DN_Title <- pad_with_na(DN_Title, max_length)
DN_RevName <- pad_with_na(DN_RevName, max_length)
DN_RevDate <- pad_with_na(DN_RevDate, max_length)
DN_UserRating <- pad_with_na(DN_UserRating, max_length)
DN_TitleRev <- pad_with_na(DN_TitleRev, max_length)
DN_TextRev <- pad_with_na(DN_TextRev, max_length)


DN_Df <- data.frame(
  Tv_Shows = DN_Title,
  Reviewer_Name = DN_RevName,
  Reviewer_Date = DN_RevDate,
  Reviewer_Rating = DN_UserRating,
  Title_Review = DN_TitleRev,
  Text_Review = DN_TextRev
)

head(DN_Df)


```
4th Link
```{r}

pad_with_na <- function(vec, target_length) {
  if (length(vec) < target_length) {
    return(c(vec, rep(NA, target_length - length(vec))))
  } else {
    return(vec)
  }
}

A_Link <- "https://www.imdb.com/title/tt11126994/reviews?ref_=tt_urv"
session2 <- bow(A_Link, user_agent = "Educational Purposes")


A_Title <- scrape(session2) %>%
  html_nodes(".parent a") %>%
  html_text()

A_RevName <- scrape(session2) %>%
  html_nodes(".display-name-link") %>%
  html_text()

A_RevDate <- scrape(session2) %>%
  html_nodes("span.review-date") %>%
  html_text()

A_UserRating <- scrape(session2) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()

A_TitleRev <- scrape(session2) %>%
  html_nodes("a.title") %>%
  html_text() %>%
  gsub("\n ", "", .)

A_TextRev <- scrape(session2) %>%
  html_nodes("div.text") %>%
  html_text()


max_length <- max(
  length(A_Title),
  length(A_RevName),
  length(A_RevDate),
  length(A_UserRating),
  length(A_TitleRev),
  length(A_TextRev)
)

A_Title <- pad_with_na(A_Title, max_length)
A_RevName <- pad_with_na(A_RevName, max_length)
A_RevDate <- pad_with_na(A_RevDate, max_length)
A_UserRating <- pad_with_na(A_UserRating, max_length)
A_TitleRev <- pad_with_na(A_TitleRev, max_length)
A_TextRev <- pad_with_na(A_TextRev, max_length)


A_Df <- data.frame(
  Tv_Shows = A_Title,
  Reviewer_Name = A_RevName,
  Reviewer_Date = A_RevDate,
  Reviewer_Rating = A_UserRating,
  Title_Review = A_TitleRev,
  Text_Review = A_TextRev
)

head(A_Df)



```
5th Link
```{r}


pad_with_na <- function(vec, target_length) {
  if (length(vec) < target_length) {
    return(c(vec, rep(NA, target_length - length(vec))))
  } else {
    return(vec)
  }
}

FP_Link <- "https://www.imdb.com/title/tt2092588/reviews?ref_=tt_urv"
session2 <- bow(FP_Link, user_agent = "Educational Purposes")


FP_Title <- scrape(session2) %>%
  html_nodes(".parent a") %>%
  html_text()

FP_RevName <- scrape(session2) %>%
  html_nodes(".display-name-link") %>%
  html_text()

FP_RevDate <- scrape(session2) %>%
  html_nodes("span.review-date") %>%
  html_text()

FP_UserRating <- scrape(session2) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()

FP_TitleRev <- scrape(session2) %>%
  html_nodes("a.title") %>%
  html_text() %>%
  gsub("\n ", "", .)

FP_TextRev <- scrape(session2) %>%
  html_nodes("div.text") %>%
  html_text()


max_length <- max(
  length(FP_Title),
  length(FP_RevName),
  length(FP_RevDate),
  length(FP_UserRating),
  length(FP_TitleRev),
  length(FP_TextRev)
)

FP_Title <- pad_with_na(FP_Title, max_length)
FP_RevName <- pad_with_na(FP_RevName, max_length)
FP_RevDate <- pad_with_na(FP_RevDate, max_length)
FP_UserRating <- pad_with_na(FP_UserRating, max_length)
FP_TitleRev <- pad_with_na(FP_TitleRev, max_length)
FP_TextRev <- pad_with_na(FP_TextRev, max_length)


FP_Df <- data.frame(
  Tv_Shows = FP_Title,
  Reviewer_Name = FP_RevName,
  Reviewer_Date = FP_RevDate,
  Reviewer_Rating = FP_UserRating,
  Title_Review = FP_TitleRev,
  Text_Review = FP_TextRev
)

head(FP_Df)
```
3. Create a time series graph for the tv shows released by year. Which year has the most number of tv
shows released?
```{r}
library(ggplot2)
library(dplyr)

ggplot(TopTv_df, aes(x = Year, fill = Year)) +
  geom_bar() +
  labs(title = "Number of TV Shows Released by Year",
       x = "Year",
       y = "Number of TV Shows") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
axis.text.x = element_text(angle = 44, hjust = 1))



cat("The year with the most number of tv shows is", TopTv_df$Year[1])
```
############  Extracting Amazon Product Reviews #################

4. Select 3 products from Amazon of the same category. Extract the price, description, ratings and
reviews of each product.
```{r}
install.packages("rvest")
install.packages("dplyr")
install.packages("polite")
install.packages("tidyverse")

library(rvest)
library(dplyr)
library(polite)
library(tidyverse)
```
#First Item
```{r}
Item1 <- "www.amazon.com/KOLIGHT-Cosmetic-Eyeliner-Eyebrow-Foundation/dp/B083GQMJS3/ref=pd_bxgy_img_d_sccl_2/139-6261811-2017508?pd_rd_w=p5DcZ&content-id=amzn1.sym.839d7715-b862-4989-8f65-c6f9502d15f9&pf_rd_p=839d7715-b862-4989-8f65-c6f9502d15f9&pf_rd_r=VQMPW6JGJE4D8WY4HF1G&pd_rd_wg=uQwwk&pd_rd_r=36fd8edc-d84b-4674-95d0-6e1a38e953d8&pd_rd_i=B083GQMJS3&psc=1"

session1 <- html_session(Item1, user_agent = "Educational Purposes")

price1 <- session1 %>%
  html_nodes('span.a-offscreen') %>%
  html_text() %>%
  trimws()
price1[1]

description1 <- session1 %>%
  html_nodes('span.a-size-large.product-title-word-break') %>%
  html_text() %>%
  trimws()
description1

prodrating1 <- session1 %>%
  html_nodes('.a-icon-star .a-icon-alt') %>%
  html_text() %>%
  trimws()
prodrating1[1]

prodreview1 <- session1 %>%
  html_nodes('#acrCustomerReviewText') %>%
  html_text() %>%
  trimws()
prodreview1[1]
```
#SECOND ITEM
```{r}
Item2 <- "www.amazon.com/dp/B0CBRSM8Z7/ref=sspa_dk_detail_0?psc=1&pd_rd_i=B0CBRSM8Z7&pd_rd_w=g6DUy&content-id=amzn1.sym.eb7c1ac5-7c51-4df5-ba34-ca810f1f119a&pf_rd_p=eb7c1ac5-7c51-4df5-ba34-ca810f1f119a&pf_rd_r=9346KSWZF27HZTP30BC4&pd_rd_wg=ZVkL8&pd_rd_r=65ae9544-f4dc-4ced-b642-7d658888adea&s=beauty&sp_csd=d2lkZ2V0TmFtZT1zcF9kZXRhaWw"

session2 <- html_session(Item2, user_agent = "Educational Purposes")

price2 <- session2 %>%
  html_nodes('span.a-offscreen') %>%
  html_text() %>%
  trimws()
price2[1]

description2 <- session2 %>%
  html_nodes('span.a-size-large.product-title-word-break') %>%
  html_text() %>%
  trimws()
description2

prodrating2 <- session2 %>%
  html_nodes('.a-icon-star .a-icon-alt') %>%
  html_text() %>%
  trimws()
prodrating2[1]

prodreview2 <- session2 %>%
  html_nodes('#acrCustomerReviewText') %>%
  html_text() %>%
  trimws()
prodreview2[1]
```
# THIRD ITEM
```{r}
Item3 <- "www.amazon.com/dp/B0BWYFYMZX/ref=sspa_dk_detail_8?psc=1&pf_rd_p=eb7c1ac5-7c51-4df5-ba34-ca810f1f119a&pf_rd_r=9346KSWZF27HZTP30BC4&pd_rd_wg=ZVkL8&pd_rd_w=g6DUy&content-id=amzn1.sym.eb7c1ac5-7c51-4df5-ba34-ca810f1f119a&pd_rd_r=65ae9544-f4dc-4ced-b642-7d658888adea&s=beauty&sp_csd=d2lkZ2V0TmFtZT1zcF9kZXRhaWw"

session3 <- html_session(Item3, user_agent = "Educational Purposes")

price3 <- session3 %>%
  html_nodes('span.a-offscreen') %>%
  html_text() %>%
  trimws()
price3[1]

description3 <- session3 %>%
  html_nodes('span.a-size-large.product-title-word-break') %>%
  html_text() %>%
  trimws()
description3

prodrating3 <- session3 %>%
  html_nodes('.a-icon-star .a-icon-alt') %>%
  html_text() %>%
  trimws()
prodrating3[1]

prodreview3 <- session3 %>%
  html_nodes('#acrCustomerReviewText') %>%
  html_text() %>%
  trimws()
prodreview3[1]
```